R Notebook

### 2019-09-06 DATA608/hw1.rmd
More work on hw1

---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

**Principles of Data Visualization and Introduction to ggplot2**

@@

@@

```
```{r}

@@

*First let's start with some aggregate counts of the data:*

@@

*Hmmm.  There are 52 states in the data set.  I'm guessing there is DC but I wonder if there is an error in the data.  I will take a closer look at this:*

```{r, comment=NA}
unique(inc$State)
```

*Ahh!  There's Puerto Rico.  My hunch about DC was correct.  No need to clean that up.  Great!*

*I am wondering how some of the variables differ the industry.  I will look at the size of the work force and the revenue.  I will also construct an output per worker to see which industry is the most productive in economic terms:*

@@

*This is not supprising that the top industries are the most "productive."  They are very capital intensive.*

@@

```{r, fig.height=10}
library(ggplot2)
library(ggthemes)

inc %>%
  group_by(State) %>%
  tally() %>%
  ggplot(aes(x = n, y=reorder(State, n))) +
  geom_point() +
  ggtitle("Number of Fastest Growing Companies by State") +
  ylab(element_blank()) + 
  xlab("Companies") + 
  theme_clean()
```

@@

```{r, warning=FALSE}
inc %>%
  filter(State == "NY") %>%
  select(Industry, Employees) %>%
  na.omit() %>%
  group_by(Industry) %>%
  mutate(Median = median(Employees)) %>%
  ggplot(aes(x = reorder(Industry, Median), y = Employees)) +
  ylim(0, 1000) +
  xlab(element_blank()) + 
  ggtitle("Workforce Size by Industry", subtitle = "(employment over 1,000 not shown)") +
  geom_boxplot(outlier.colour="gray", outlier.shape=8, outlier.size = 0.9) +
  coord_flip() +
  theme_clean()
```

@@

*Funny!  I guess I think like this investor.*

```{r, warning=FALSE}
inc %>%
  select(Industry, Revenue, Employees) %>%
  na.omit() %>%
  mutate(`Revenue Per Employee` = Revenue / Employees / 1000000) %>%
  group_by(Industry) %>%
  mutate(Median = median(`Revenue Per Employee`, na.rm = TRUE)) %>%
  ggplot(aes(x = reorder(Industry, Median), y = `Revenue Per Employee`)) +
  ylim(0, 1) +
  xlab(element_blank()) + 
  ylab("Millions of Dollars") + 
  ggtitle("Revenue per Employee by Industry", subtitle = "(revenue over $1MM not shown)") +
  geom_boxplot(outlier.colour="gray", outlier.shape=8, outlier.size = 0.9) +
  coord_flip() +
  theme_clean()
```

>>>>

---
title: "R Notebook"
output:
  html_document:
    code_folding: "hide"
  html_notebook: default
---
```{r}
library(knitr)
# A Prefix nulling hook.

# Make sure to keep the default for normal processing.
default_output_hook <- knitr::knit_hooks$get("output")

# Output hooks handle normal R console output.
knitr::knit_hooks$set( output = function(x, options) {

  comment <- knitr::opts_current$get("comment")
  if( is.na(comment) ) comment <- ""
  can_null <- grepl( paste0( comment, "\\s*\\[\\d?\\]" ),
                     x, perl = TRUE)
  do_null <- isTRUE( knitr::opts_current$get("null_prefix") )
  if( can_null && do_null ) {
    # By default R print output aligns at the right brace.
    align_index <- regexpr( "\\]", x )[1] - 1
    # Two cases: start or newline
    re <- paste0( "^.{", align_index, "}\\]")
    rep <- comment
    x <- gsub( re, rep,  x )
    re <- paste0( "\\\n.{", align_index, "}\\]")
    rep <- paste0( "\n", comment )
    x <- gsub( re, rep,  x )
  }

  default_output_hook( x, options )

})

knitr::opts_template$set("kill_prefix"=list(comment=NA, null_prefix=TRUE))
```
**Principles of Data Visualization and Introduction to ggplot2**

@@

```{r comment=NA}

@@

```
```{r comment=NA}

@@

**First let's start with some aggregate counts of the data:**

@@

**Hmmm.  There are 52 states in the data set.  I'm guessing there is DC but I wonder if there is an error in the data.  I will take a closer look at this:**

```{r, comment=NA, null_prefix=TRUE}
unique(inc$State)
```

**Ahh!  There's Puerto Rico.  My hunch about DC was correct.  No need to clean that up.  Great!**

**I am wondering how some of the variables differ the industry.  I will look at the size of the work force and the revenue.  I will also construct an output per worker to see which industry is the most productive in economic terms:**

@@

**This is not supprising that the top industries are the most "productive."  They are very capital intensive.**

@@

```{r, fig.height=10}
library(ggplot2)

inc %>%
  group_by(State) %>%
  tally() %>%
  ggplot(aes(x = n, y=reorder(State, n))) +
  geom_point(color = "dodger blue") +
  labs(title = "Number of Fastest Growing Companies by State",
       y = element_blank(),
       x = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray95"),
        panel.grid.major.x = element_line(color = "gray95", linetype="dashed"))
```

@@

```{r, warning=FALSE}
inc %>%
  filter(State == "NY") %>%
  select(Industry, Employees) %>%
  na.omit() %>%
  group_by(Industry) %>%
  mutate(Median = median(Employees)) %>%
  ggplot(aes(x = reorder(Industry, Median), y = Employees)) +
  ylim(0, 1000) +
  labs(title = "Workforce Size by Industry",
       subtitle = "(employment over 1,000 not shown)",
       y = element_blank(),
       x = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray95"),
        panel.grid.major.x = element_line(color = "gray95", linetype="dashed")) +
  geom_boxplot(outlier.colour="gray", outlier.shape = 8, outlier.size = 0.9) +
  coord_flip()
```

@@

**Funny!  I guess I think like this investor.**

```{r, warning=FALSE}
inc %>%
  select(Industry, Revenue, Employees) %>%
  na.omit() %>%
  mutate(`Revenue Per Employee` = Revenue / Employees / 1000000) %>%
  group_by(Industry) %>%
  mutate(Median = median(`Revenue Per Employee`, na.rm = TRUE)) %>%
  ggplot(aes(x = reorder(Industry, Median), y = `Revenue Per Employee`)) +
  ylim(0, 1) +
  labs(title = "Revenue per Employee by Industry", 
       subtitle = "(revenue over $1MM not shown)",
       y = "Millions of Dollars",
       x = element_blank()) +
  theme(panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray95"),
        panel.grid.major.x = element_line(color = "gray95", linetype="dashed")) +
  geom_boxplot(outlier.colour="gray", outlier.shape = 8, outlier.size = 0.9) +
  coord_flip()
```
